---
title: "Cluster_comparisons"
author: "Maria Secara"
date: "2025-09-01"
output: html_document
---

# Internal Clustering Validation  
## Comparing consensus clustering to determine the optimal cluster number moving forwards

### Clusters range from 2-8. Dunn's index and silhouette width will be plotted to determine the optimal cluster number  
  
avg.silwidth = average silhouette width (want higher)
dunn = minimum separation / maximum diameter  
dunn2 = minimum average dissimilarity between two cluster / maximum average within cluster dissimilarity
widestgap = widest within-cluster gap
sindex = separation index
wb.ratio = average.within/average.between

```{r}
#load in the necessary libraries 
library(dplyr)
library(ggplot2)
#install.packages("ggalluvial")
library(ggalluvial)
```


```{r}
#change to split 2 if running replication
clust_parameters_2 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_2.csv", sep=",")
clust_parameters_3 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_3.csv", sep=",")
clust_parameters_4 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_4.csv", sep=",")
clust_parameters_5 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_5.csv", sep=",")
clust_parameters_6 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_6.csv", sep=",")
clust_parameters_7 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_7.csv", sep=",")
clust_parameters_8 <- read.csv(".../SNF_output1/full_Cluster_fit_stats_8.csv", sep=",")

# Merge the data frames into one
clust_parameters <- bind_rows(
  clust_parameters_2 %>% mutate(Cluster = 2),
  clust_parameters_3 %>% mutate(Cluster = 3),
  clust_parameters_4 %>% mutate(Cluster = 4),
  clust_parameters_5 %>% mutate(Cluster = 5),
  clust_parameters_6 %>% mutate(Cluster = 6),
  clust_parameters_7 %>% mutate(Cluster = 7),
  clust_parameters_8 %>% mutate(Cluster = 8)
)

```
  
```{r echo=FALSE, fig.height=5, fig.width=5}
## plot average silhouette plot 
parameters <- clust_parameters[which(clust_parameters$X == "avg.silwidth" | clust_parameters$X == "dunn" |  clust_parameters$X == "sindex" | clust_parameters$X == "wb.ratio"), ]

ggplot(parameters, aes(x = factor(Cluster), y = unlist.cluster_stats., group = X)) +
  geom_point(size = 1) +
  geom_line()+
  facet_wrap(~ X, scales = "free_y") + # Create separate plots for each fit index
  labs(title = "Cluster Fit Indices for c = 2-8",
       x = "Number of Clusters (C)",
       y = "Fit Index Value") +
  theme_classic() +
  theme(legend.position = "none") # Optional: Remove the legend if it's not needed
Input_directory = ".../SNF_output1/cluster_comparison/"
ggsave(last_plot(), file=paste(Input_directory, "Goodness_of_fit.png", sep=""))

```

```{r}
# Extract cluster assignments from each SNF model
snf2 <-read.csv(".../SNF_output1/train_RESULTS_2_clust_k34_0.7.csv")
snf3 <-read.csv(".../SNF_output1/train_RESULTS_3_clust_k34_0.7.csv")
snf4 <-read.csv(".../SNF_output1/train_RESULTS_4_clust_k34_0.7.csv")
snf5 <-read.csv(".../SNF_output1/train_RESULTS_5_clust_k34_0.7.csv")
snf6 <-read.csv(".../SNF_output1/train_RESULTS_6_clust_k34_0.7.csv")
snf7 <-read.csv(".../SNF_output1/train_RESULTS_7_clust_k34_0.7.csv")
snf8 <-read.csv(".../SNF_output1/train_RESULTS_8_clust_k34_0.7.csv")


df1 <- snf2[,c(2,3)] %>% rename(SNF2 = groups)
df2 <- snf3[,c(2,3)] %>% rename(SNF3 = groups)
df3 <- snf4[,c(2,3)] %>% rename(SNF4 = groups)
df4 <- snf5[,c(2,3)] %>% rename(SNF5 = groups)
df5 <- snf6[,c(2,3)] %>% rename(SNF6 = groups)
df6 <- snf7[,c(2,3)] %>% rename(SNF7 = groups)
df7 <- snf8[,c(2,3)] %>% rename(SNF8 = groups)

# Merge datasets by pin
df <- purrr::reduce(list(df1, df2, df3, df4, df5, df6, df7), left_join, by = "participant_id")
# Convert to long format
df_long <- df %>%
  tidyr::pivot_longer(cols = starts_with("SNF"),
               names_to = "Model",
               values_to = "Cluster") %>%
  mutate(Model = as.factor(gsub("SNF", "", Model)),  # Convert Model to factor
         Cluster = as.factor(Cluster))  # Ensure Cluster is categorical
# Check structure
str(df_long)
# Set color palette based on max number of clusters
num_clusters <- length(unique(df_long$Cluster))
palette_colors <- RColorBrewer::brewer.pal(n = min(num_clusters, 12), name = "Set1")  # Use up to 12 colors
# Alluvial plot
ggplot(df_long, aes(x = Model, stratum = Cluster, alluvium = participant_id, fill = Cluster)) +
  ggalluvial::geom_flow(stat = "alluvium", alpha = 0.7) +  # Flow connections
  ggalluvial::geom_stratum(alpha = 0.8) +  # Cluster strata
  scale_x_discrete(limits = as.character(2:8)) +  # Ensure all models appear
  scale_fill_manual(values = palette_colors) +  # Apply custom color palette
  labs(title = "Changes in Class Membership Across SNF Models",
       x = "Number of Classes in Model",
       y = "Count of Individuals") +
  theme_minimal()
```